When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases

### 2018-02-19 paper/paper.tex
Cite thesis (review 1)
Sample size (review 1)

Parts of this paper were presented at IJCAI \citep{DBLP:conf/ijcai/McCreeshPT16}; the first three
sections have been expanded, whilst
\cref{section:regular,section:labelled,section:filterverify} are new material.

@@

    \caption{With a fixed pattern graph order of 20, a target graph order of 150, a target edge
    probability of 0.40, and varying pattern edge probability, we observe a phase transition and
    complexity peak with the Glasgow solver in the non-induced variant. Each point $(x, y)$
    represents one instance $i$, where $x$ is the pattern edge probability used to generate $i$, $y$
    is the number of search nodes needed by the Glasgow solver to solve $i$, and the point is drawn
    as a green circle if $i$ is satisfiable, and a blue cross otherwise. The black line plots the
    evolution of the mean number of search nodes when increasing the pattern edge probability from
    $0$ to $1$.}
    \label{figure:phase-transition}
\end{figure}

>>>>

Parts of this paper were presented at IJCAI \citep{DBLP:conf/ijcai/McCreeshPT16}; the first three
sections have been expanded, whilst
\cref{section:regular,section:labelled,section:filterverify} are new material. Most of this work
also appeared in a PhD thesis \citep{o:McCreesh17}.

@@

    \caption{With a fixed pattern graph order of 20, a target graph order of 150, a target edge
    probability of 0.40, and varying pattern edge probability, we observe a phase transition and
    complexity peak with the Glasgow solver in the non-induced variant. Each point $(x, y)$
    represents one instance $i$, where $x$ is the pattern edge probability used to generate $i$, $y$
    is the number of search nodes needed by the Glasgow solver to solve $i$, and the point is drawn
    as a green circle if $i$ is satisfiable, and a blue cross otherwise. The black line plots the
    evolution of the mean number of search nodes when increasing the pattern edge probability from
    $0$ to $1$ in steps of $0.01$, using a larger sample size of $1,000$.}
    \label{figure:phase-transition}
\end{figure}
